\section{Introduction} \slabel{intro}

The Rayleigh-Taylor instability has been the subject of considerable study since its characterization by Lord Rayleigh in the 19th century~\cite{Rayleigh1883}.
Despite this, many aspects of the non-linear growth remain poorly understood.
Analytic models based on potential flow have been reasonably effective for flows with a large density jump, \ie an Atwood number, $\Delta \rho / \sum \rho$, near unity~\cite{Layzer1955, Layzer1955}.
However, recent experiments at low Atwood number have demonstrated a significant departure from the potential flow limit:
Rayleigh-Taylor bubbles are seen accelerating past the terminal velocity predicted by potential flow models~\cite{Wilkinson2007}.
The acceleration persists beyond times which are experimentally accessible, so numerous efforts have been made to compute the late time flow numerically~\cite{Ramaprabhu2012,Wei2012}.
Ultimately, the goal is to use these numerical experiments to inform a simple model that captures the key features of the flow, as potential flow models do for high Atwood number flows.

This study concerns the dynamics of the single-mode Rayleigh-Taylor instability (smRTI), where the interface between a heavy fluid and a light fluid is perturbed with a single wavelength $\lambda$ and corresponding wavenumber $k$.
If the Atwood number is low, then at early times the interface grows exponentially with a rate given by a linear approximation~\cite{Duff1962}:
\begin{equation} \elabel{duff0}
\gamma = \sqrt{\frac{A g k}{1 + \pi^{-1/2} k \delta} + \nu^2 k^4} - (\nu + D) k^2,
\end{equation}
where $A$ is the Atwood number,
$g$ is the local acceleration,
$\delta$ is the interface thickness,
$\nu$ is the kinematic viscosity, and
$D$ is the diffusivity.
As the amplitude approaches the wavelength, the linear growth saturates.
At unit Atwood number, the non-linear regime is described by potential flow, in which Layzer~\cite{Layzer1955} found the interface approaches a terminal velocity proportional to the root of the acceleration and wavelength: $v_L \sim \sqrt{g \lambda}$:
Potential flow models have been extended $A < 1$, with the most successful model by Goncharov~\cite{Goncharov2002}:
\begin{equation} \elabel{goncharov}
v_G = \frac{1}{\sqrt{\pi}} \sqrt{\frac{A g \lambda}{1+A}}
\end{equation}

Experiments by Wilkinson and Jacobs~\cite{Wilkinson2007} show that after reaching the velocity given by \eref{goncharov}, low Atwood bubbles unexpectedly accelerate a second time.
This is termed `re-acceleration`, with the terminal velocity replaced by a `stagnation velocity`.
Re-acceleration was not present in popular potential flow and buoyancy-drag models, and attempts to capture re-acceleration have been the emphasis of recent model development in the low Atwood number regime.

Experiments have thus far been unable to observe more than the onset of the re-acceleration phase.
Therefore, the community has turned to numerical studies to compute late-time dynamics.
At least two such efforts have been under-taken, one by Ramaprabu \etal~\cite{Ramaprabhu2012} and one by Wei and Livescu~\cite{Wei2012}, leading to slightly different conclusions.
In the study by Ramaprabhu, the flow accelerates to around twice the stagnation velocity and then decelerates back to the stagnation velocity, indicating that re-acceleration may be a transient.
In the study by Wei and Livescu, the flow re-accelerates and then breaks up into many small pockets of buoyant fluid, which themselves continue to accelerate at nearly a fixed rate.

Buoyancy-drag models have been proposed for the multi-mode and single-mode dynamics of the bubble front.
They balance the buoyant force of the bubble with a drag force to predict the front velocity as a function of the characteristic length.
Ramaprabhu proposes an additional forcing term based on the development of a vortex ring at the bubble tip, but relies on observation of the mean vorticity experimentally or in numerical simulations.
There is a need for a predictive model for re-acceleration that relies only on the initial conditions.

In \sref{model}, we propose a simple buoyancy-drag model for the dynamics of the smRTI.
In \sref{exp}, we present a battery of numerical trials.
In \sref{late}, we describe the regimes present in late time bubble trajectories.
In \sref{fit}, we fit the unconstrained model coefficients to the numerical results..
Finally, in \sref{conc}, we assess the current state of smRTI and highlight outstanding questions.

