\section{Growth stages through late times}

In the spirit of recent analyses~\cite{Ramaprabhu2012, Wei2012}, we try to identify growth stages.

For low Rayleigh numbers, the bubble stagnates before reaching the top of the computational domain.

For high Rayleigh numbers, the bubble grows until it begins to interact with the finite height domain.
The affected trajectories are therefore incomplete.

Some of the coefficients, specifically $C_7$ and $C_2$, have increasing effects late in the bubble growth.
Therefore, the incomplete trajectories are relatively underconstrained in these parameters, i.e. the trajectory is relatively insensetive to their values.


\subsection{Expoential growth}
When the amplitude is small and the interface is thin, the linear theory, simple model, and numerical results all identify exponential growth: $\ddot{h} = \gamma^2 h$.
The simple model differs from the linear theory by the absence of a $-D k^2$ term, which is the only term that can cause unstable interfaces to decay, i.e. $\gamma < 0$ for positive Atwood numbers.
In the simple model, all unmixed bubbles grow while in the lineary theory highly diffusive bubbles decay.

\subsection{Stagnation}



\subsection{Mixing}
As the bubble height increases, so does the surface area of the bubble.
When the viscous drag reduces the bubble's acceleration, the flux of pure fluid into the bubble, which goes as the velocity, is unable to math the flux of mixed fluid through the interface.



\subsection{Penetration depth}

The penetration depth is the maximum height of the bubble, which is the height of the bubble at the stopping condition of this analysis.
The pentration depth depends strongly on the Rayleigh number and is nearly independent of the Schmidt number, as shown in \fref{depth_scatter}.
Furthermore, the relationship to the Rayleigh number is linear over the cases shown here, as shown in \fref{depth_line}.

