\documentclass[twocolumn,showpacs,preprintnumbers,amsmath,amssymb,floatfix]{revtex4-1}
\usepackage{mysty}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage{pgfplotstable}
%\usepackage{booktabs}
\usepackage{array}
\usepackage{colortbl}
\usepackage{dashrule}

%\usepackage[caption=false]{subfig}

\begin{document}

\title{Data-driven modeling of the low-Atwood single-mode Rayleigh-Taylor instability}

\author{Maxwell Hutchinson}
\affiliation{The Physics Department, University of Chicago, Chicago IL 60637}
\email{maxhutch@uchicago.edu}

\date{\today}

\begin{abstract}
The Rayleigh-Taylor instability (RTI) pervades classical fluid dynamics and is essential to a diversity of phenomena, e.g. salt fingers, thermonuclear flames, and inertial confinement fusion, but remains poorly understood in dissipative systems.
Recently, the single-mode RTI has shown experimentally and numerically to deviate from established potential flow models when the Atwood number was less than $1/2$.
Attempts to explain the deviation, termed re-acceleration, have been ad-hoc and hindered by a dearth of data at late times and high aspect ratios.
This paper present buoyancy-drag and mixing models that include dissipative terms and match the linear theory.
To inform the model, a numerical experiment is performed, simulating a range of Grashof and Schmidt numbers and reaching bubble heights 34$\times$ the bubble width.
The model coefficients are estimated by physical argument and then fit to the numerical results.
The model error is less than 2\% for the bubble height and 4\% for the volume of mixed fluid.
An attempt is made to interpret variations in the fit parameters with the Rayleigh and Schmidt numbers, where present, but it is hindered by many of the simulations interacting with the boundaries.
Simulations in higher aspect ratio domains would improve the model.
\end{abstract}

\pacs{}
\maketitle

\input{toc}

\bibliography{library}

\end{document}

